### 2017-03-01 intro.tex
Finished all of intro re-write save for 1.3

As gas does begin to cool within these halos, it will lose pressure support (by
radiating away thermal energy), but {\it not} angular momentum.  For large
spiral galaxies, this means that the baryons, which typically carry the same
specific angular momentum as the halo itself, will flatten to form an
exponential disc as they cool \citep{Fall1980,Mo1998}.    A combination
of heating and cooling processes will render this gas multiphase, containing
both warm/hot ($T>10^4\;\rm{K}$) and cold ($T\sim10-100\;\rm{K}$) gas in
quasistatic equilibrium \citep{McKee1977}.  This multiphase state is highly
dependent on both the metallicity and the local heating rates (which
themselves can vary with redshift) \citep{Field1969,Wolfire1995,Norman1997}.  In
the disc of the galaxy, this dense multiphase gas forms the ISM from which stars
collapse and are born.
\begin{figure}
    \includegraphics[width=0.7\textwidth]{mass_function.eps}
    \caption[Galaxy mass function]{The observed mass function for galaxies in
    the nearby universe (derived using abundance matching for the solid line and
    semi-analytic modelling for the green points) does not match the mass
    function for dark matter halos given in equation 1, scaled by the baryon
    fraction (dashed line).  This tells us that there are additional physical
    processes involved in the formation of galaxies within their dark matter
    halos.  The most likely candidate for this is feedback from stars and black
    holes.  Of particular interest is the peak in star formation efficiency near
    $M_{200}=10^{12}M_\odot$.  \textit{Image credit: Adapted from figure 1 in
    \citet{Ferrero2012}}}.
\end{figure}

@@

The earliest numerical simulations of galaxy formation focused on the effects of
gravity alone.  A classic example of this are the simulations presented in
\citet{Toomre1972}, which showed that the irregular structures seen in galaxies
like NGC 4676 (``The Mice'') or NGC4038/4039 (``The Antennae Galaxies'') are the
results of major mergers between two disc galaxies, as is clear from figure 1.2.
These simulations used discs composed of a mere 120 test particles, and ignored
the effects of self-gravity between these particles.  Despite their crudeness,
these simulations definitively showed that the morphologies of galactic bridges and tails could be
formed by the tidal interactions of two passing/merging galaxies.  The IBM
360/95 that \citet{Toomre1972} (with an inflation-adjusted purchase price in the
millions of dollars) used for their simulations was capable of 5.5 million
instructions per second, roughly $0.2\%$ the speed of a \$35 Raspberry Pi 3
available today.

@@

\subsection{Hydrodynamics}
Hydrodynamical solvers usually come in one of two classes: Eulerian or
Lagrangian.  Eulerian methods discretize space into fixed volume elements with
fixed boundaries.  By breaking a simulation volume into a grid of cells that
each contains scalar and vector quantities those quantities can be advected
between cells according to the solver scheme.  Eulerian schemes typically allow
for higher-order solvers, lower intrinsic noise, and better resolved
discontinuities \citep{Teyssier2002,Stone2008,Bryan2014}.  They suffer from
intrinsic mixing and diffusion that scales with the flow velocity relative to
the grid, poor integration of circular orbits, and costly timestep limits
\citep{Agertz2007,Tasker2008}.  Lagrangian methods instead discretize mass,
breaking the gaseous volume into discrete points, each of which moves at the
fluid velocity to advect the quantities it contains, with smoothing functions
used to interpolate values in between particles; hence the name for the most
common Lagrangian method, Smoothed Particle Hydrodynamics (SPH).  Lagrangian
methods couple easily to tree and particle-mesh codes for gravity calculation,
are Galilean invariant, and intrinsically conserve mass, energy, and momentum
(linear and angular) \citep{Katz1996,Wadsley2004,Springel2005}.  The perfect
conservation of angular momentum is critical for accurately tracking orbits. SPH
requires the use of artificial viscosity to handle shocks, and as such have
difficulty in capturing subsonic turbulence \citep{Bauer2012}. Recently, new
methods have begin to hybridize features of each of these classes as well
\citep{Springel2010,Hopkins2015}.

@@

\subsection{Designing Simulations}
Beyond the choice of algorithms, the construction of appropriate inital
conditions is also important.  To study large populations of galaxies, along
with large-scale structure, large-volume cosmological boxes with volumes
$\gtrsim 10^6\;\rm{Mpc^3}$, but with spatial resolutions $\sim \rm{kpc}$ are
used (for example, the {\it Illustris} simulations have a softening length of
$1.4\;rm{kpc}$ \citealt{Vogelsberger2014}).  Studying how individual galaxies
form is typically done with cosmological zoom simulations, where a comparatively
cheap dark-matter only simulation is first run to select a region of interest,
which is then resimulated with higher resolution and baryonic physics included
\citep{Navarro1993}. Zoom-in simulations can typically achieve an order of
magnitude or better resolution than full cosmological boxes.  Isolated galaxy
disc simulations use a constructed disc profiles containing gas and stars,
embedded within a dark halo. These cannot show how galaxies form in a
cosmological environment, but can be run with $\sim \rm{pc}$ resolution to study
closely how internal processes within a galaxy take place
\citep{Hopkins2011,Benincasa2016}.  Details of these internal processes are
discussed in section 1.3.

The earliest attempt to track the formation of a galaxy in a cosmological
context with the effects of star formation and feedback included was by
\citet{Katz1992}.  This simulation used the Lagrangian TREESPH 
\citep{Hernquist1989} to evolve a volume of gas and dark matter from an initial
linear perturbation, including small-scale power derived from CDM predictions
\citep{Zeldovich1970,Peebles1982}.  Gas was allowed to cool radiatively using
rates calculated for primordial gas.  This study introduced a model for star
formation that is still the standard for most simulations of galaxy formation.
Observations \citep{Kennicutt1998} have suggested that the star formation rate
is a power law of the gas density: $\dot\Sigma_*\propto\Sigma_{gas}^\alpha$, with
$\alpha=1-2$.  If it is assumed that gas collapses to form stars in some
multiple $c_*$ of its freefall time \citep{Schmidt1959}, $t_{ff}$, a simple
3-dimensional star formation model can be built with the form:
\begin{equation}
    \dot\rho_* = \frac{c_*\rho_{gas}}{t_{ff}} = c_*\sqrt{\frac{\rho^3_{gas}}{4\pi G}}
\end{equation}
\citet{Katz1992} used a $c_*$ parameter of $0.1$, which is within the range of
what is typically used in simulations today ($1-100\%$).  On top of the model
for star formation, feedback was included without the use of any significant
subgrid model:  $10^{51}\;\rm{erg/SN}$ worth of energy was injected back into
the ISM by smoothing it over a number of resolution elements.  One of the key
findings of \citet{Katz1992} was that the vast majority of SN energy was
radiated away, making them very ineffective at regulating star formation within
the galaxy.  In the end, \citet{Katz1992} found that the peak star formation in
the simulated galaxy was nearly 10 times greater than in observed galaxies.
\citet{Thacker2000} later showed that the smoothing of energy used by
\citet{Katz1992} resulted in a large overestimation of the cooling rates in
feedback-heated gas. Since then, much work has gone into developing models for
feedback that address the issue of overcooling that was present in these
earlier simulations.

\section{The Importance of Feedback}
\begin{figure}
    \includegraphics[width=\textwidth]{M82.eps}
	\caption[Massive outflows in M82]{The evidence for feedback is no clearer
	than here in the Cigar Galaxy, M82.  The Hubble Space Telescope reveals massive
	outflows of hot ionized gas through the red $H\alpha$ emission as gas is
	blasted out of the galaxy in a bipolar flow. \textit{Image credit: NASA, ESA
	and the Hubble Heritage Team STScI/AURA}}
\end{figure}
We now have strong evidence that galaxy and star formation is not a one way process of
gravitational collapse.  A number of internal processes (``feedback'') within
galaxies can liberate energy greater than the gravitational binding energy of
molecular clouds (and indeed even comparable to the binding energy of the entire
halo).  Analytic calculations that omit feedback processes found that gas should
rapidly collapse into the smallest halos at high redshift, overproducing
stars in small galaxies at high redshift (the ``cooling catastrophe'')
\citep{Cole2001,Benson2003}.  Simulations of galaxies like our own develop unrealistically
compact morphologies without feedback \citep{Stinson2006}.  Without feedback, simulations of
individual molecular clouds have star formation rates an order of magnitude
too high \citep{Agertz2013}.  Aside from regulating star formation and the
growth of galaxies, there are also observations of the large-scale impact of
feedback. Lyman $\alpha$ forest observations probing the intergalactic medium
(IGM) have found that the IGM is polluted with metal ions at great distances
from any galaxies \citep{Sargent1988,Songaila1996,Dave1998}.  These metals must have
been ejected by galactic outflows from the ISM of galaxies where they formed.
As figure 1.3 shows, fast, massive outflows have been observed leaving the ISM of
starburst galaxies and quasar host galaxies \citep{Veilleux2005,Werk2014}.

The two primary sources of feedback energy are massive stars and supermassive
black holes (SMBHs).  Massive stars ($M>5M_\odot$) experience short, violent
lives.  During their lives, they will drive fast $v>1000\;\rm{km/s}$ stellar
winds \citep{Weaver1977}, and heat their surrounding gas with UV radiation
\citep{Krumholz2009}.  At the end of their lives, $4-30\;\rm{Myr}$ later, these
stars die in energetic core-collapse SN, liberating $\sim10^{51}\;\rm{erg}$
\citep{Wilson1985,Bethe1990}.  Figure 1.4 shows the total budget of available
energy liberated by a population of stars.  The energy released by a population
of stars with solar metallicity is $\sim 2\times10^{51}\;\rm{erg/M_\odot}$.
Most of this energy is released as photons, over the lifetime of each star.
These will couple poorly to the surrounding ISM, and so have little impact on
disrupting all but the densest gas.  While stellar winds typically have
comparable luminosity to supernovae, they occur for an order of magnitude less
time ($\sim4$ Myr vs. $\sim40$ Myr).  This means that supernovae, despite only
contributing $\sim1\%$ of the total energy released by a stellar population, may
have the greatest impact on galactic scales.  This energy imparts heat and
momentum to the surrounding ISM, and can accelerate cosmic rays in the shocks
that result \citep{Bell1978}.  In galaxies with actively growing SMBHs, the
accretion disc that forms as gas funnels into the black hole can reach
temperatures exceeding $10^9\;\rm{K}$ through viscous heating
\citep{Antonucci1993}.  This makes these accretion discs some of the most
luminous objects in the universe, and can heat the gas that surrounds the galaxy
to choke off the accretion of gas onto the galaxy, shutting off star formation.

@@

The coupling of feedback energy to the ISM is what determines the effectiveness
of that feedback.  In the lowest mass galaxies, UV photoheating may be the
primary regulator of star formation \citep{Efstathiou1992}.    However, UV
radiation has characteristic temperatures too low to drive galactic winds.
Large {\sc Hii} regions, such as 30 Doradus, have observed expansion rates of
only $25\;\rm{km/s}$ \citep{Chu1994}, far below the velocities needed to drive
galaxy-scale outflows.  Radiation pressure on dust grains has been suggested as
a driving mechanism for outflows \citep{Murray2011}.  Simulations of
radiation-driven galactic winds have thus far relied on major approximations
\citep{Roskar2014,Agertz2015} and questionably large infrared optical depths
\citep{Hopkins2014}.  The porosity of the ISM likely means that the vast
majority of UV photons are able to escape without imparting significant energy
or momentum \citep{Dale2005,Walch2012,Krumholz2013}.

On top of releasing just $10\%$ of the energy released by supernovae, stellar
winds are active during the early stages of a massive star's life.  This means
that these winds are released into the dense natal gas that massive star
clusters form in.  Stellar wind shocks within this dense molecular gas cool
efficiently, leading to much of the stellar wind energy being lost to radiation
that escapes the ISM completely.  Simulations of molecular clouds with feedback
from star clusters \citep{Gendelev2012,Rogers2013} have found that most stellar
wind energy is expended disrupting the molecular clouds the clusters live in.
While these winds do not significantly escape the cluster, the channels they
open within the cloud allow $\sim99\%$ of SN energy to escape the dense
molecular environment.

On the galactic scale, feedback regulates star formation in two primary ways.
Energy and momentum deposited into the ISM can heat and disrupt the cool clouds
of gas which form stars \citep{Rogers2013}, and increase the ISM scale height to
limit the formation of cool clouds out of the warm ISM
\citep{Ostriker2010,Benincasa2016}.  If that feedback is vigorous enough, this
gas can actually be ejected from the disc into the circum-galactic medium (CGM)
\citep{Larson1974,Heckman1987,Hopkins2012b}.  This limits star formation by
simply removing the fuel for the process.  These outflows are needed to explain
observations of low star formation efficiencies in massive galaxies
\citep{Behroozi2013,Moster2013}, observations of outflowing gas
\citep{Lynds1963,Heckman1987}, a metal-polluted intergalactic medium
\citep{Shen2010}, and the low bulge fraction in star forming galaxies
\citep{Brook2012}.  In order to see how the local deposition of feedback energy
drives these winds, simulations with realistic models for hot stellar feedback
are required.

\subsection{Numerical Challenges for Hot Feedback}
The greatest difficulty with including the effects of feedback in simulations of
galaxy evolution is the combination of extreme energy gradients in a relatively
small mass/volume.  Without overwhelmingly high resolution, hot feedback gas
will be numerically mixed with cold ISM, often resulting in gas with
temperatures of $\sim10^5\;\rm{K}$, at the peak of the ISM cooling curve where
cooling times are extremely short.  This results in feedback energy being
completely lost due to radiative cooling, as was first seen by \citet{Katz1992}.
Indeed, as \citet{Thacker2000} showed, how feedback energy is deposited into the
ISM has a huge impact on whether that feedback has any effect.  This problem has
been tackled using a few different strategies.

Since overcooling is the problem, many models have attacked this directly by
either temporarily disabling cooling \citep{Thacker2000,Stinson2006} or
depositing feedback energy into a second, nonthermal energy component
\citep{Agertz2013}.  While this does limit radiative losses, it produces gas
that exists in an unphysical region of the $\rho-T$ phase diagram, which may not
have the correct entropy to escape buoyantly.  It also has the potential to
introduce an \textit{undercooling} problem as resolution becomes higher and
feedback-heated gas becomes resolvable.  Alternatively, energy may be injected
not as heat, but as momentum, which naturally does not cool
\citep{Scannapieco2006,DallaVecchia2008,Dubois2008}.  Unfortunately, this adds
the additional complexity of momentum cancellation (how to treat neighbouring
stars/clusters, where two stars are depositing momentum with opposing
directions), and if this momentum results in strong shocks, these shocks will
convert the momentum right back into thermal energy that can radiate away the
feedback energy the model is designed to preserve \citep{Durier2012}.  This
often means kinetic/momentum feedback models must be combined with hydrodynamic
decoupling that renders feedback-heated gas into a form that does not interact
with the surrounding ISM \citep{Springel2003,Vogelsberger2013}.  Naturally, this
makes outflow properties strongly influenced by numerical choices
\citep{DallaVecchia2008}.  A third choice is to stochastically deposit feedback
energy only when enough energy is available to produce gas temperatures high
enough for cooling times to be short \citep{DallaVecchia2012,Crain2015}.  In
these models, SN events are effectively grouped together, somewhat decoupling
feedback spatially from star formation.  The choice of temperature to heat gas
to is a purely numerical parameter, and can dramatically change the
effectiveness of these models.  Finally, some \citep{Springel2003,Murante2015}
attempt to directly address the unphysical numerical mixing of hot and cold gas
by separating the two phases and tracking each component separately.  This
completely solves the overcooling problem, and allows the two components to cool
radiatively.   Unfortunately, it also means that cold star-forming gas is
permanently coupled to hot feedback-heated gas: preventing the simulation of  a
resolved multiphase ISM, and effectively making the ISM an anchor holding down
potential hot outflows.  This means these multiphase models have to be coupled
with parameterized models to capture outflows \citep{Springel2003}.  Often,
these simple models simply choose a fraction of feedback energy to be deposited
as kinetic ``kicks'' to a some gas particles.  Like other kinetic feedback
models, this is frequently combined with hydrodynamical decouplings
\citep{Vogelsberger2013}.

All of these models attempt to solve the problem of overcooling with unphysical
approximations: disabled cooling, hydrodynamic decoupling, stochastic deposition
of feedback energy, and imposed multiphase ISM models.  These choices make it
difficult to understand what details of simulated galaxy evolution are a result
of these numerical free parameters, as opposed to the actual physics of
self-regulated star formation and SN-driven outflows.  What is needed is a model that
captures the effects of feedback while matching as closely as possible the
actual physical processes involved below the resolution scale.

>>>>

As gas does begin to cool within these halos, it will lose pressure support (by
radiating away thermal energy), but {\it not} angular momentum.  For large
spiral galaxies, this means that the baryons, which typically carry the same
specific angular momentum as the halo itself, will flatten to form an
exponential disc as they cool \citep{Fall1980,Mo1998}.    A combination
of heating and cooling processes will render this gas multiphase, containing
both warm/hot ($T>10^4\;\rm{K}$) and cold ($T\sim10-100\;\rm{K}$) gas in
quasistatic equilibrium \citep{McKee1977}.  This multiphase state is highly
dependent on both the metallicity and the local heating rates (which
themselves can vary with redshift) \citep{Field1969,Wolfire1995,Norman1997}.  In
the disc of the galaxy, this dense multiphase gas forms the ISM from which stars
collapse and are born.

The formation of stars has a dramatic impact on the galaxy.  As molecular clouds
begin to construct O/B stars with masses $>5\Msun$, these stars immediately
begin to obliterate the clouds from which they form.  A typical $10^5\Msun$
cluster will have an ionizing UV luminosity of $\sim10^5\Lsun$ during its first
few Myr of life.  This UV flux ionizes the surrounding gas, heating it to
$\sim10^4\;\rm{K}$ \citep{Dale2005,Murray2011}.  Along with ionizing radiation,
massive stars drive fast $v>10^3\kms$ stellar winds, further shocking and
destroying the cold, dense gas which stars form from.  By the time the most
massive stars reach the end of their short lives, $\sim4$ Myr later, they
detonate as core-collapse supernovae not in dense ($n>100\hcc$) clouds, but in
their significantly more diffuse remnants \citep{Rogers2013}.  The longer
cooling times this results in allows supernovae to expand through the ISM,
driving turbulance \citep{Ostriker2010} and filling most of the volume with hot,
diffuse gas.  Much of this hot gas is in fact able to leave the ISM, driven out
as hot, buoyant, high-entropy gas.  These feedback-driven outflows remove gas
from the disc, slowing the rate of star formation, and polluting the
intergalactic medium with metals from stellar ejecta.  In the most massive
galaxies ($M>10^{12}\Msun$), these outflows can be driven by the accretion
luminosity of the central supermassive black hole (SMBH).  These Active Galactic
Nuclei (AGN) are observed in giant elliptical galaxies, and can be seen blowing
hot bubbles within the intracluster medium of nearby galaxy clusters.  Further
discussion on feedback can be found in section~\ref{intro:fb}.

\begin{figure}
    \includegraphics[width=0.7\textwidth]{mass_function.eps}
    \caption[Galaxy mass function]{The observed mass function for galaxies in
    the nearby universe (derived using abundance matching for the solid line and
    semi-analytic modelling for the green points) does not match the mass
    function for dark matter halos given in equation 1, scaled by the baryon
    fraction (dashed line).  This tells us that there are additional physical
    processes involved in the formation of galaxies within their dark matter
    halos.  The most likely candidate for this is feedback from stars and black
    holes.  Of particular interest is the peak in star formation efficiency near
    $M_{200}=10^{12}M_\odot$.  \textit{Image credit: Adapted from figure 1 in
    \citet{Ferrero2012}}}.
\end{figure}

@@

The earliest numerical simulations of galaxy formation focused on the effects of
gravity alone.  A classic example of this are the simulations presented in
\citet{Toomre1972}, which showed that the irregular structures seen in galaxies
like NGC 4676 (``The Mice'') or NGC4038/4039 (``The Antennae Galaxies'') are the
results of major mergers between two disc galaxies, as is clear from figure 1.2.
These simulations used discs composed of a mere 120 test particles, and ignored
the effects of self-gravity between these particles.  Despite their crudeness,
these simulations showed that the morphologies of galactic bridges and tails could be
formed by the tidal interactions of two passing/merging galaxies.  The IBM
360/95 that \citet{Toomre1972} (with an inflation-adjusted purchase price in the
millions of dollars) used for their simulations was capable of 5.5 million
instructions per second, roughly $0.2\%$ the speed of a \$35 Raspberry Pi 3
available today.

@@

\subsection{Hydrodynamics}
Hydrodynamical solvers usually come in one of two classes: Eulerian or
Lagrangian.  Eulerian methods discretize space into fixed volume elements with
fixed boundaries.  By breaking a simulation volume into a grid of cells that
each contains scalar and vector quantities those quantities can be advected
between cells according to the solver scheme.  Eulerian schemes typically allow
for higher-order solvers, lower intrinsic noise, and better resolved shocks
(when at rest relative to the grid) \citep{Teyssier2002,Stone2008,Bryan2014}.
They suffer from intrinsic mixing and diffusion that scales with the flow
velocity relative to the grid, poor integration of circular orbits, and costly
timestep limits \citep{Agertz2007,Tasker2008}.  A variety of Eulerian solvers
exist, ranging from the staggered mesh, high-order upwind \& artificial
viscosity scheme ZEUS, used in codes such as {\sc ENZO}
\citep{Stone1999,Bryan2014}, to the 2nd order Godunov method MUSCL used by {\sc
ramses} \citep{vanLeer1976,Teyssier2002}, or the 3rd order PPM scheme of {\sc
Athena} \citep{Stone2008}.  Lagrangian methods instead discretize mass, breaking
the volume into discrete points, each of which moves at the fluid
velocity to advect the quantities it contains, with smoothing functions used to
interpolate values in between particles; hence the name for the most common
Lagrangian method, Smoothed Particle Hydrodynamics (SPH).  Lagrangian methods
couple easily to tree and particle-mesh codes for gravity calculation, are
Galilean invariant, and intrinsically conserve mass, energy, and momentum
(linear and angular) \citep{Katz1996,Wadsley2004,Springel2005}.  The perfect
conservation of angular momentum is critical for accurately tracking orbits. SPH
methods typically use artificial viscosity to handle shocks, and as such have
difficulty in capturing subsonic turbulence \citep{Bauer2012}.  Recently, new
methods have begin to extend the basic SPH method using higher order gradient
estimates that are allowing accuracy on subsonic tests that rival the best
Eulerian schemes \citep{Springel2010,Hopkins2015,Valdarnini2016}.

@@

\subsection{Designing Simulations}
Beyond the choice of algorithms, the construction of appropriate inital
conditions is also important.  To study large populations of galaxies, along
with large-scale structure, large-volume cosmological boxes with volumes
$\gtrsim 10^6\;\rm{Mpc^3}$, but with spatial resolutions $\sim \rm{kpc}$ are
used (for example, the {\it Illustris} simulations have a softening length of
$1.4\;rm{kpc}$ \citealt{Vogelsberger2014}).  Studying how individual galaxies
form is typically done with cosmological zoom simulations, where a comparatively
cheap dark-matter only simulation is first run to select a region of interest,
which is then resimulated with higher resolution and baryonic physics included
\citep{Navarro1993}. Zoom-in simulations can typically achieve an order of
magnitude or better resolution than full cosmological boxes.  A number of groups
today are using these zoom-in simulations to study the impact of feedback
processes over cosmic time \citep{Stinson2013,Hopkins2014,Agertz2015}.  Isolated
galaxy disc simulations use a constructed disc profiles containing gas and
stars, embedded within a dark halo. These cannot show how galaxies form in a
cosmological environment, but can be run with $\sim \rm{pc}$ resolution to study
closely how internal processes within a galaxy take place
\citep{Hopkins2011,Benincasa2016}.  Details of these internal processes are
discussed in section 1.3.

The earliest attempt to track the formation of a galaxy in a cosmological
context with the effects of star formation and feedback included was by
\citet{Katz1992}.  This simulation used the Lagrangian TREESPH 
\citep{Hernquist1989} to evolve a volume of gas and dark matter from an initial
linear perturbation, including small-scale power derived from CDM predictions
\citep{Zeldovich1970,Peebles1982}.  Gas was allowed to cool radiatively using
rates calculated for primordial gas.  This study introduced a model for star
formation that is still the standard for most simulations of galaxy formation.
Observations \citep{Kennicutt1998} have suggested that the star formation rate
is a power law of the gas density: $\dot\Sigma_*\propto\Sigma_{gas}^\alpha$, with
$\alpha=1-2$.  If it is assumed that gas collapses to form stars in some
multiple $c_*$ of its freefall time \citep{Schmidt1959}, $t_{ff}$, a simple
3-dimensional star formation model can be built with the form:
\begin{equation}
    \dot\rho_* = \frac{c_*\rho_{gas}}{t_{ff}} = c_*\sqrt{\frac{\rho^3_{gas}}{4\pi G}}
\end{equation}
\citet{Katz1992} used a $c_*$ parameter of $0.1$, which is within the range of
what is typically used in simulations today ($1-100\%$).  On top of the model
for star formation, feedback was included without the use of any significant
subgrid model:  $10^{51}\;\rm{erg/SN}$ worth of energy was injected back into
the ISM by smoothing it over a number of resolution elements.  One of the key
findings of \citet{Katz1992} was that the vast majority of SN energy was
radiated away, making them very ineffective at regulating star formation within
the galaxy.  In the end, \citet{Katz1992} found that the peak star formation in
the simulated galaxy was nearly 10 times greater than in observed galaxies.
\citet{Thacker2000} later showed that the smoothing of energy used by
\citet{Katz1992} resulted in a large overestimation of the cooling rates in
feedback-heated gas. Since then, much work has gone into developing models for
feedback that address the issue of overcooling that was present in these
earlier simulations.  These efforts will be described in detail in the next
section.

\section{The Importance of Feedback}\label{intro:fb}
\begin{figure}
    \includegraphics[width=\textwidth]{M82.eps}
	\caption[Massive outflows in M82]{The evidence for feedback is no clearer
	than here in the Cigar Galaxy, M82.  The Hubble Space Telescope reveals massive
	outflows of hot ionized gas through the red $H\alpha$ emission as gas is
	blasted out of the galaxy in a bipolar flow. \textit{Image credit: NASA, ESA
	and the Hubble Heritage Team STScI/AURA}}
\end{figure}
Evidence has been building for decades that galaxy and star formation is not a
one way process of gravitational collapse.  A number of internal processes
(feedback) within galaxies can liberate energy greater than the gravitational
binding energy of molecular clouds (and indeed even comparable to the binding
energy of the entire halo).  Analytic calculations that omit feedback processes
found that gas should rapidly collapse into the smallest halos at high redshift,
overproducing stars in small galaxies at high redshift (the ``cooling
catastrophe'') \citep{Cole2001,Benson2003}.  
Simulated galaxies develop unrealistically compact morphologies without feedback
\citep{Stinson2006}.  Without feedback, simulations of individual molecular
clouds have star formation rates an order of magnitude too high
\citep{Agertz2013}.  Aside from regulating star formation and the growth of
galaxies, there are also observations of the large-scale impact of feedback.
Lyman $\alpha$ forest observations probing the intergalactic medium (IGM) have
found that the IGM is polluted with metal ions at great distances from any
galaxies \citep{Sargent1988,Songaila1996,Dave1998}.  These metals must have been
ejected by galactic outflows from the ISM of galaxies where they formed. Figure
1.3 shows a composite image of the dwarf starburst M82, where fast, massive
outflows have been seen leaving the ISM.  These outflows have been observed as a
ubiquitous feature of starburst galaxies and quasar host galaxies
\citep{Veilleux2005,Werk2014}.

The two primary sources of feedback energy are massive stars and SMBHs.  Massive
stars ($M>5M_\odot$) experience short, violent lives.  Prior to their death,
they will drive fast $v>1000\;\rm{km/s}$ stellar winds \citep{Weaver1977}, and
ionize their surrounding gas with UV radiation \citep{Krumholz2009}.  At the end
of their lives, $4-30\;\rm{Myr}$ later, these stars die in energetic
core-collapse SN, liberating $\sim10^{51}\;\rm{erg}$
\citep{Wilson1985,Bethe1990}.  Figure 1.4 shows the total budget of available
energy liberated by a population of stars with a standard \citet{Chabrier2003}
IMF.  The total energy released by a population of stars with solar metallicity is
$\sim 2\times10^{51}\;\rm{erg/M_\odot}$.  Most of this energy is released as
photons, over the lifetime of each star.  These will couple poorly to the
surrounding ISM, and so have little impact on disrupting all but the densest
gas.  While stellar winds typically have comparable luminosity to supernovae,
they occur for an order of magnitude less time ($\sim4$ Myr vs. $\sim40$ Myr).
This means that supernovae, despite only contributing $\sim1\%$ of the total
energy released by a stellar population, may have the greatest impact on
galactic scales.  This energy imparts heat and momentum to the surrounding ISM,
and can accelerate cosmic rays in the shocks that result \citep{Bell1978}.  In
galaxies with actively growing SMBHs, the accretion disc that forms as gas
funnels into the black hole can reach temperatures exceeding $10^9\;\rm{K}$
through viscous heating \citep{Antonucci1993}.  This makes these accretion discs
some of the most luminous objects in the universe, and can heat the gas that
surrounds the galaxy to choke off the accretion of gas onto the galaxy, shutting
off star formation.

@@

The coupling of feedback energy to the ISM is what determines the effectiveness
of that feedback.  In the lowest mass galaxies, UV photoheating may be the
primary regulator of star formation \citep{Efstathiou1992}.    However, UV
radiation has characteristic temperatures too low to drive galactic winds.
Large {\sc Hii} regions, such as 30 Doradus, have observed expansion rates of
only $25\;\rm{km/s}$ \citep{Chu1994}, far below the velocities needed to drive
galaxy-scale outflows.  Radiation pressure on dust grains has been suggested as
a driving mechanism for outflows \citep{Murray2011}.  Simulations that see a
large effect from radiation-driven galactic winds have thus far relied on major approximations
\citep{Roskar2014,Agertz2015} and questionably large infrared optical depths
\citep{Hopkins2014}.  Without high optical depths and multiple scattering, UV
photons will be reprocessed to IR that escape before imparting significant
energy or momentum to the surrounding gas \citep{Dale2005,Walch2012,Krumholz2013}.

On top of releasing just $10\%$ of the energy released by supernovae, stellar
winds are active during the early stages of a massive star's life.  This means
that these winds are released into the dense natal gas that massive star
clusters form in.  Stellar wind shocks within this dense molecular gas cool
efficiently, leading to much of the stellar wind energy being lost to radiation
that escapes the ISM completely.  Simulations of molecular clouds with feedback
from star clusters \citep{Gendelev2012,Rogers2013} have found that most stellar
wind energy is expended disrupting the molecular clouds the clusters live in.
While these winds (along with radiation pressure and UV-heated gas) do not
significantly escape the cluster, the channels they open within the cloud allow
a large fraction of SN energy to escape the dense molecular environment, while
the energy from winds and radiation are expended in disrupting the cloud.

On the galactic scale, feedback regulates star formation in two primary ways.
Energy and momentum deposited into the ISM can heat and disrupt the cool clouds
of gas which form stars \citep{Rogers2013}, and increase the ISM scale height to
limit the formation of cool clouds out of the warm ISM
\citep{Ostriker2010,Benincasa2016}.  If that feedback is vigorous enough, gas
can actually be ejected from the disc into the circumgalactic medium (CGM)
\citep{Larson1974,Heckman1987,Hopkins2012b}.  Even if this material is still
bound to the halo, it can take $\sim\;\rm{Gyr}$ to return to the ISM.  This
limits star formation by simply removing the fuel for the process.  These
outflows are needed to explain observations of low star formation efficiencies
in massive galaxies \citep{Behroozi2013,Moster2013}, observations of outflowing
gas \citep{Lynds1963,Heckman1987}, a metal-polluted intergalactic medium
\citep{Shen2010}, and the low bulge fraction in star forming galaxies
\citep{Brook2012}.  In order to see how the local deposition of feedback energy
drives these winds, simulations with realistic models for hot stellar feedback
are required.

\subsection{Numerical Challenges for Hot Feedback}
The greatest difficulty with including the effects of feedback in simulations of
galaxy evolution is the combination of extreme gradients of temperature,
density, and velocity all in a relatively small mass/volume.  Without
overwhelmingly high resolution, hot feedback gas will be numerically mixed with
cold ISM, often resulting in gas with temperatures of $\sim10^5\;\rm{K}$, at the
peak of the ISM cooling curve where cooling times are extremely short.  This
results in feedback energy being completely lost due to radiative cooling, as
was first seen by \citet{Katz1992}.  Indeed, as \citet{Thacker2000} showed, how
feedback energy is deposited into the ISM has a huge impact on whether that
feedback has any effect.  This problem has been tackled using a few different
strategies.

Since overcooling is the problem, many models have attacked this directly by
either temporarily disabling cooling \citep{Thacker2000,Stinson2006} or
depositing feedback energy into a second, nonthermal energy component
\citep{Agertz2013}.  While this does limit radiative losses, it produces gas
that exists in an unphysical region of the $\rho-T$ phase diagram, which may not
have the correct entropy to escape buoyantly.  It also has the potential to
introduce an \textit{undercooling} problem as resolution becomes higher and
feedback-heated gas becomes resolvable.  Alternatively, energy may be injected
not as heat, but as momentum, which naturally does not cool
\citep{Navarro1993,Mihos1994,Scannapieco2006,DallaVecchia2008,Dubois2008}.
Unfortunately, this adds the additional complexity of momentum cancellation (how
to treat neighbouring stars/clusters, where two stars are depositing momentum
with opposing directions), and if this momentum results in strong shocks, these
shocks will convert the momentum right back into thermal energy that can radiate
away the feedback energy the model is designed to preserve \citep{Durier2012}.
This often means kinetic/momentum feedback models must be combined with
hydrodynamic decoupling that renders feedback-heated gas into a form that does
not interact with the surrounding ISM \citep{Springel2003,Vogelsberger2013}.
Naturally, this makes outflow properties strongly influenced by numerical
choices \citep{DallaVecchia2008}.  A third choice is to stochastically deposit
feedback energy only when enough energy is available to produce gas temperatures
high enough for cooling times to be short \citep{DallaVecchia2012,Crain2015}.
In these models, SN events are effectively grouped together, somewhat decoupling
feedback spatially from star formation.  The choice of temperature to heat gas
to is a purely numerical parameter, and can dramatically change the
effectiveness of these models.  Finally, some \citep{Springel2003,Murante2015}
attempt to directly address the unphysical numerical mixing of hot and cold gas
by separating the two phases and tracking each component separately.  This
completely solves the overcooling problem, and allows the two components to cool
radiatively.   Unfortunately, it also means that cold star-forming gas is
permanently coupled to hot feedback-heated gas: preventing the simulation of  a
resolved multiphase ISM, and effectively making the cold/warm ISM an anchor
holding down potential hot outflows.  This means these multiphase models have to
be coupled with parameterized models to capture outflows \citep{Springel2003}.
Often, these simple models simply choose a fraction of feedback energy to be
deposited as kinetic ``kicks'' to a some gas particles.  Like other kinetic
feedback models, this is frequently combined with hydrodynamical decouplings
\citep{Vogelsberger2013}.

All of these models attempt to solve the problem of overcooling with unphysical
approximations: disabled cooling, hydrodynamic decoupling, stochastic deposition
of feedback energy, and imposed multiphase ISM models.  These choices make it
difficult to understand what details of simulated galaxy evolution are a result
of these numerical free parameters, as opposed to the actual physics of
self-regulated star formation and SN-driven outflows.  What is needed is a model
that captures the effects of feedback while matching as closely as possible the
actual physical processes involved below the resolution scale.  Simulations that
rely on numerically-motivated, complex subgrid models are devoid of serious
predictive power.  When the results obtained depend heavily of the tuning of
multiple free parameters, those results can at best probe one point in the space
of the possible, rather than hew away at that space to discover the region of
the probable, and ultimately, the truth.  As Von Neumann famously quipped to
Fermi, ``With four parameters I can fit an elephant, and with five I can make
him wiggle his trunk.''
